A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-29 4_method.tex
shorten paragraph about polygon domains

\tim{Below is taken from an outdated paragraph in section 3.3 (?)}
The trapezoids are classified as belonging to a specific domain following \citeauthor{Ding2016a}.
Each polygon in the input shape acquires it's own domain.
The domains of hole polygons are touching the domains of the outer polygon.
See \cref{shape_decomposition_domains}.

Each of the trapezoids is connecting to a single outline polygon.
By traversing the trapezoids in the domain of each outline polygon in order we can efficiently connect all segments into polylines.
See \cref{segment_generation}.
In a final step we connect the ends of polylines together, so that the final toolpaths contain both polygons and polylines.

>>>>

All trapezoids in the ST can be assigned to separate domains, corresponding to which boundary polygon they are connected to (see \cref{shape_decomposition_domains})~\cite{Ding2016a}.
By traversing the trapezoids in per domain in order we can efficiently connect all segments into polylines.
See \cref{segment_generation}.
In a final step we connect the ends of polylines together, so that the final toolpaths contain both polygons and polylines.
